%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plasmati Graduate CV
% LaTeX Template
% Version 1.0 (24/3/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati (alessandro.plasmati@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template needs to be compiled with XeLaTeX.
% The main document font is called Fontin and can be downloaded for free
% from here: http://www.exljbris.com/fontin.html
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper,10pt]{ctexart} % Default font size and paper size

\usepackage{fontspec} % For loading fonts
\defaultfontfeatures{Mapping=tex-text}
\setmainfont{Helvetica Neue}
\setsansfont{Times New Roman}
\setmonofont{Courier New}
\setCJKmainfont{Noto Sans CJK SC}
\setCJKsansfont{Noto Serif CJK SC}
\setCJKmonofont{Noto Sans Mono CJK SC}

\usepackage{xunicode,xltxtra,url,parskip} % Formatting packages

\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors

% \usepackage[big]{layaureo} % Margin formatting of the A4 page, an alternative to layaureo can be \usepackage{fullpage}
% To reduce the height of the top margin uncomment: \addtolength{\voffset}{-1.3cm}
\usepackage{fullpage}

\usepackage{hyperref} % Required for adding links	and customizing them
\definecolor{linkcolour}{rgb}{0,0,0} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\Large\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{3pt}{6pt} % Spacing around sections
\titleformat{\subsection}{\large\raggedright}{ -}{0.2em}{} % Text formatting of subsections
\titlespacing{\subsection}{0pt}{0pt}{3pt} % Spacing around subsections

\usepackage{makecell}
\usepackage{array}
\usepackage{tabularx}
\usepackage{longtable}

\usepackage{fontawesome5}

\usepackage{enumitem}
\setenumerate[1]{itemsep=3pt,partopsep=0pt,parsep=0pt,topsep=3pt}
\setitemize[1]{itemsep=3pt,partopsep=0pt,parsep=0pt,topsep=3pt}
\setdescription{itemsep=3pt,partopsep=0pt,parsep=0pt,topsep=3pt}

\begin{document}

\pagestyle{empty} % Removes page numbering

\font\fb=''[cmr10]'' % Change the font of the \LaTeX command under the skills section


%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{center}
    {\LARGE Haoran Dang}（党浩然） \\
    \faIcon{envelope} \  \href{mailto:danghr@outlook.com}{danghr@outlook.com} \  / \  \faIcon{desktop} \  \href{https://www.danghr.com}{danghr.com} \\
\end{center}


%----------------------------------------------------------------------------------------
%	EDUCATION INFO
%----------------------------------------------------------------------------------------

\section{EDUCATION}

    \begin{itemize}
        \item \textbf{Institute of Computing Technology, Chinese Academy of Sciences} \hfill Sep 2022 - Present \\
        M.Eng Student in Electronic Information \hfill Beijing, China \\
        \begin{small}
            Supervisor: Prof. Dongrui Fan \quad
            GPA: 3.81/4 \quad
        \end{small}
        \item \textbf{ShanghaiTech University} \hfill Sep 2018 - Jun 2022\\
        B.Eng in Computer Science and Technology \hfill Shanghai, China \\
        \begin{small}
            GPA: 3.50/4 \quad Rank in major: 55/194 (28.4\%) \quad
       \end{small}
    \end{itemize}


%----------------------------------------------------------------------------------------
%	RESEARCH WORK
%----------------------------------------------------------------------------------------

\section{RESEARCH}

    \subsection{Papers \& Articles}

        \begin{itemize}
            \item \underline{H Dang}, M Wu, M Yan, X Ye, and D Fan, ``\textbf{GDL-GNN: Applying GPU Dataloading of Large Datasets for Graph Neural Network Inference},'' to be published in \textit{Euro-Par 2024}.
            \item \underline{H Dang}, C Ye, Y Hu, and C Wang, ``\textbf{NobLSM: An LSM-tree with Non-blocking Writes for SSDs},'' \textit{DAC 2022}. DOI: \href{https://doi.org/10.1145/3489517.3530470}{10.1145/3489517.3530470}.
            \item D Wang, M Yan, Y Teng, D Han, \underline{H Dang}, X Ye, and D Fan, ``\textbf{A Transfer Learning Framework for High-accurate Cross-workload Design Space Exploration of CPU},'' \textit{ICCAD 2023}. DOI: \href{https://doi.org/10.1109/ICCAD57390.2023.10323840}{10.1109/ICCAD57390.2023.10323840}
        \end{itemize}

    \subsection{Research Experience}

    \begin{itemize}
        \item \textbf{Lab of Graph Intelligent Machine} \quad HTCRC, SKLP, ICT, CAS \hfill Dec 2021 - Present \\
        {\small Director: Assoc. Prof. Mingyu Yan} \hfill Beijing, China
        \begin{small}
            \begin{itemize}
                \item Conducted research to accelerate GNN inference on multi-GPU platforms, developed and implemented an optimized GPU dataloading method based on partition, achieving a 59.9\% performance improvement over baseline. (cf. GDL-GNN)
                \item Developed an undergraduate FYP on optimizing GNN training, halving training times by implementing a multithreaded data loader across various GPUs. Awarded the SIST Outstanding Thesis.
            \end{itemize}
        \end{small}

        \item \textbf{Toast Lab} \quad SIST, ShanghaiTech \hfill Jul 2021 - Feb 2022 \\
        {\small Director: Assist. Prof. Chundong Wang} \hfill Shanghai, China
        \begin{small}
            \begin{itemize}
                \item Designed and implemented NobLSM's database component, using a modified ext4 interface to delay file deletions and minimize costly \textbf{\texttt{sync}}s. Demonstrated enhanced performance via benchmarking against SOTA LSM-trees. (cf. NobLSM)
            \end{itemize}
        \end{small}

        \item \textbf{Attitude Research Lab} \quad SEM, ShanghaiTech \hfill Sep 2020 - Sep 2021 \\
        {\small Director: Assoc. Prof. Lifeng Yang} \hfill Shanghai, China
        \begin{small}
            \begin{itemize}
                \item Participated in preparation of the book \textit{Ethics and Morality in Information Science and Technology}. Provided suggestions on publishing houses and 
            \end{itemize}
        \end{small}
    \end{itemize}


%----------------------------------------------------------------------------------------
%	TEACHING
%----------------------------------------------------------------------------------------

\section{TEACHING}

    \begin{itemize}
        \item \textbf{Operating System I} (TA) \hfill ShanghaiTech \quad Fall, AY 2021-2022
    \end{itemize}


%----------------------------------------------------------------------------------------
%	LANGUAGE AND STANDARDIZED TESTS
%----------------------------------------------------------------------------------------

\section{LANGUAGE \& STANDARDIZED TESTS}

    \begin{itemize}
        \item \textbf{TOEFL iBT} \quad Score: 107 \hfill Apr 2024 \\
        \begin{small}
            Reading: 29 \quad Listening: 27 \quad Speaking: 23 \quad Writing: 28
        \end{small}
        \item \textbf{GRE General Test} \quad Score: 328 \hfill Aug 2022 \\
        \begin{small}
            Verbal Reasoning: 158 \quad Quantitative Reasoning: 170 \quad Analytical Writing: 4
        \end{small}
        \item \textbf{College English Test Band 6 (CET-6)} \quad Score: 572 \hfill Jun 2021 \\
        \begin{small}
            Listening: 198 \quad Reading: 211 \quad Writing \& Translation: 163
        \end{small}
    \end{itemize}


%----------------------------------------------------------------------------------------
%	CERTIFICATES
%----------------------------------------------------------------------------------------

\section{CERTIFICATES \& AWARDS}

    \begin{itemize}
        \item \textbf{2022 SIST Outstanding Thesis} {\small (for final year project)} \hfill ShanghaiTech \quad Jun 2022
        \item \textbf{Excellent Individual of Industrial Practice in Class of 2018} \hfill ShanghaiTech \quad Jun 2021
        \item \textbf{Excellent Individual of Social Practice in 2019} \hfill ShanghaiTech \quad Nov 2019
    \end{itemize}


%----------------------------------------------------------------------------------------
%	Service
%----------------------------------------------------------------------------------------

\section{VOLUNTARY SERVICE}

    \begin{itemize}
        \item \textbf{"Sunflower Activity" - Haidian Hospital Volunteers} \hfill ICT, CAS \quad Dec 2023
            \begin{small} \begin{itemize}
                \item Assisted the Service Center in answering patients' questions and printing pathology reports.
            \end{itemize} \end{small}
        \item \textbf{2020 Freshmen Enrollment} \hfill ShanghaiTech \quad Sep 2020
            \begin{small} \begin{itemize}
                \item Guidance in baggage claim of postgraduate students.
            \end{itemize} \end{small}
        \item \textbf{2020 Campus Opening Day} \hfill ShanghaiTech \quad Jul 2020
            \begin{small} \begin{itemize}
                \item Participated device check and exam download.
            \end{itemize} \end{small}
        \item \textbf{2019 Undergraduate Admission} \hfill ShanghaiTech \quad Jun 2019
            \begin{small} \begin{itemize}
                \item Participated in admission consultation in Beijing.
            \end{itemize} \end{small}
    \end{itemize}

\end{document}
